Paper 1 Analysis

### 2015-11-03 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Added extra models.

>>>>

<<Other_Models>>=
# PT, unadjusted kl, quality-adjusted e
mod_PT_uakl_qae <- cesModel(iGDP ~ iKstkS.L + iL + iUMP + iYear, HistoricalData$PT, nest=c(1,2,3))
# PT, quality-adjusted kl, unadjusted e
mod_PT_qakl_uae <- cesModel(iGDP ~ iKservS.L + ihLest + iXpMP + iYear, HistoricalData$PT, nest=c(1,2,3))

# UK, unadjusted kl, quality-adjusted e
mod_UK_uakl_qae <- cesModel(iGDP ~ iKstkO.WwithRD + iL + iU + iYear, HistoricalData$UK, nest=c(1,2,3))
# UK, quality-adjusted kl, unadjusted e
mod_UK_qakl_uae <- cesModel(iGDP ~ iKservO.WwithRD + ihLest + iXp + iYear, HistoricalData$UK, nest=c(1,2,3))
@

### 2015-11-03 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Added extra models.

>>>>

<<Other_Models_Results>>=
# PT, unadjusted kl, quality-adjusted e
summary(mod_PT_uakl_qae)
naturalCoef(mod_PT_uakl_qae)

# PT, quality-adjusted kl, unadjusted e
summary(mod_PT_qakl_uae)
naturalCoef(mod_PT_qakl_uae)

# UK, unadjusted kl, quality-adjusted e
summary(mod_UK_uakl_qae)
naturalCoef(mod_UK_uakl_qae)

# UK, quality-adjusted kl, unadjusted e
summary(mod_UK_qakl_uae)
naturalCoef(mod_UK_qakl_uae)
@
